---
title: "DDP Week 4 Assignment"
author: "Cherylyn Ee"
date: "11/6/2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
```

## Introduction

This presentation is part of the Course Project for Developing Data Products Week 4.
Explanation in the slides can be used as guidance for users on ways to use the Shiny application and the data used to create the Shiny application.

The app developed is available in the link below:
(https://cherylynee.shinyapps.io/DDP_CourseAssignment/)

Source code for ui.R and server.R is available in the link below:
(https://github.com/cherylyn-ee/Developing-Data-Products)

## Best Match College Finder

This app helps you to select the best match college according to criteria below:

- Outstate: No of outstate students
- Private: Public/ private college indicator
- Cost: Personal + Room & Board Costs
- Top25perc: New students from top 25 % of high school class   
- Apps: Number of applications received

The app then predicts the graduation rate based on this input and displays tab - "Predict Graduation Rate"

## College Data
Data used for the application is from "College" data from the ISLR" package. The data contains statistics for a large number of US Colleges from the 1995 issue of US News and World Report.
It has 777 observations and 18 variables of which 6 were used - Private, Outstate, Cost (Personal + Room & Board Cost), Top25perc, & Apps.
```{r college1, echo = TRUE}
library(ISLR); data("College")
head(College)
```

## Visual of Predicted Data
The method used for predicting graduation rate is 'gbm' - boosting with trees. Plot of predicted grad rate vs actual grade rate.

```{r college2, echo = FALSE, warning=FALSE, message=FALSE}
library(ISLR); data("College");library(ggplot2);
library(caret)
College2 <- College
College2$Cost <- College$Personal + College$Room.Board
intrain<-createDataPartition(y=College2$Grad.Rate, p=0.7, list=FALSE)
trainingset<-College2[intrain, ]; testingset<-College2[-intrain, ]
model1 <- train(Grad.Rate ~ Outstate + Top25perc + Apps + Cost + Private , method='gbm', data=trainingset, verbose=FALSE) 
qplot(predict(model1, testingset), Grad.Rate, data = testingset)
```

